Box 1 - TDT Curves

### 2023-09-20 ms/ms.qmd
Updates qmd to have the code to generate each new species TDTD data

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable,  patchwork, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, bayesplot, here)

@@

>>>>

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable,  patchwork, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd, multcomp, bayesplot, here, readxl)

##################################
# Functions
##################################

  source(here::here("R", "func.R"))

@@

```{r, newspp}
#| label: newspp
#| echo: false
#| message: false
#| include: false

# Load the data
  spp <- read_excel(here::here("data", "tdt_data.xlsx"), sheet = "data")

# Calcluate the TDT
  tdt <- split(spp, spp$group)

# Calculations
  txt <- plyr::ldply(lapply(tdt, function(x) tdt_calc(data = x)))

We can have a look at each new species' TDT curves collected by Vanessa (@fig-tdt). We can also use the data to calculate the TDT curve (slope) and $CT_{max}$ for each species (@tbl-1).

```{r, fig-tdt}
#| label: fig-tdt
#| fig-cap: TDT curves for each species. The x-axis is temperature and the y-axis is the log10 of the time to coma. 
#| message: false
#| echo: false

# Lets have a look at the data
  #ggplot2::ggplot(data, ggplot2::aes(x = assay_temp, y = log10(t_coma), colour = group)) + ggplot2::geom_point() + #ggplot2::facet_wrap(~group, nrow = 2, ncol = 4) +ggplot2::labs(x = "Temperature", y = "log 10 Coma Time") + #ggplot2::theme_bw()

# Fecet wrap doesn't seem to want to work
  par(mfrow=c(2,4))
  invisible(lapply(tdt, function(x) plot(log10(x$t_coma) ~ x$assay_temp,  main= unique(x$group), xlab = "Temperature", ylab = "log 10 Coma Time", pch = 16, col = "black")))
```

```{r, tbl-1}
#| label: tbl-1
#| tbl-cap: Estimated parameters for each of the 8 new species. 
flextable(txt) %>% align(align = "center", part = "all") %>% font(fontname="Times", part = "body") %>% 
    font(fontname="Times", part = "header")  %>%  autofit()
```

```{r, fig-tdt2}
```
